
\cvsection{Selected Publications}

\begin{cvparagraph}

\begin{itemize}
\item  2022. Active Choice vs. Inertia? An Exploratory Assessment of the European Microsoft Case’s Choice Screen, \textit{Journal of Competition Law and Economics}  (2022).
\item 2021. Una Introducción al Análisis Económico del Derecho (An Introduction to the Economic Analysis of Law). Valencia, Spain. \textit{Tirant lo Blanch}. Foreword by Professor A. Mitchell Polinsky. Review by Professor Florencia Marotta-Wurgler (book, whole)
\item 2021. Can Data Exploitation be Properly Addressed by Competition Law? A Note of Caution, February 2021, \textit{Concurrences} N° 1-2021, Art. N° 98791, pp. 75-82 (coauthored with Jörg Hoffmann)
\item 2021. Buyer Beware: An Exploratory Assessment of the New Chilean Food Labeling Model. \textit{Hastings International and Comparative Law Review}. V.44, 2. Summer Issue: 144-165
\end{itemize}
\begin{itemize}
\item 2020. No Alarms and Many Surprises: Salience as a Basis for Excessive Pricing Intervention in an Antitrust Context. \textit{Journal of Competition Law and Economics}. Volume 16, Issue 4, December 2020, pp. 552–571
\item  2018. Why do Most People Follow the Default Matrimonial Property Regime in Chile? \textit{Economic Analysis of Law Review}, 2018 V. 9, 2: 232-258. 
\item 2017. The Costs of Loyalty: On Loyalty Rewards and Consumer Welfare. \textit{Economic Analysis of Law Review}, V. 8, 2: 409-445. 
\end{itemize}
You may find a complete list of publications in my \href{https://omarvd.github.io}{GitHub}. 



\end{cvparagraph}




